Algomusicology, ?, Profit

### 2016-04-02 paper.tex
Format function names in monospace.

The Underpants Gnomes are renowned for their business plan:
\begin{itemize}
    \item Collect underpants
    \item ?
    \item Profit
\end{itemize}

Art critics, literary critics, algomusicologists and Twitter have a challenge in common with the Underpants Gnomes - we may have
collected a considerable quantity of underpants/art/users, but how are we to turn that into profit? Less glibly, is algomusicology
doomed to be a mere observer and explainer of musical practice, or might it become an active participant? Computer science is
able to influence industry, though that might take longer than we'd like \footnote{Alonzo Church developed the
lambda calculus in the 1930s. Java gained lambda expressions in 2015.}. Can algomusicology influence music?\footnote{This paper
appears to be the first reference to algomusicology. I believe the term, which is a portmanteau of algorave and musicology,
has a self-evident definition.}

@@

The examples in this paper are all written in Clojure, dialect of Lisp. I also rely on Leipzig, a music theory library written
in Clojure and Midje, a unit testing library, for its fact notation.

@@

Though storing such a string would require roughly a petabyte of memory, representing it indirectly as a computation
takes very little space at all. To put it in perspective, that's roughly the size all music ever recorded to date,
described in less than a half a tweet\footnote{Based on the iTunes library featuring approximately 50 million songs
of approximately 4 megabytes each, and assuming it represents approximately a fifth of all recorded music. Tweets are
restricted to 140 characters.}.

We can use Clojure's macro facility to build a crude framework for comparing the size of descriptions and their
resulting values. The following two definitions are identical, save that description-length is a macro and therefore
operates on the unevaluated s-expression passed to it as an argument.

@@

If there is no way to describe a value more concisely than the value itself, we say that it is random. An explanatory
power of one or less is no explanation at all.

@@

Using a little more macro magic, we can calculate the ratio between the above description and the literal notes
of the song. The definitional macro allows us to use the symbol row-row in our fact notation, rather than having to
paste in the entire expression.

>>>>

The South Park Underpants Gnomes are renowned for their business plan:
\begin{enumerate}
    \item Collect underpants
    \item ?
    \item Profit
\end{enumerate}

A common interpretation of the Gnomes' business is as a satire on Silicon Valley startups. Art critics, literary critics,
algomusicologists and start-uppers have a challenge in common with the Underpants Gnomes
- we may have collected a considerable quantity of underpants/art/users, but how are we to turn that into profit?

Less glibly, is algomusicology doomed to be a mere observer and explainer of musical practice, or might it become an
active participant? Computer science is able to influence industry, though that might take longer than we'd like.
\footnote{Alonzo Church developed the lambda calculus in the 1930s. Java gained lambda expressions in 2015.} Can
algomusicology influence music?\footnote{This paper appears to be the first reference to algomusicology. I believe the term,
which is a portmanteau of algorave and musicology, has a self-evident definition.}

@@

The examples in this paper are all written in Clojure, a dialect of Lisp. I also rely on Leipzig, a music theory library,
and Midje, a unit testing library.\footnote{Midje allows us to write a unit test as (fact expression => result),
which asserts that expression evaluates to result.}

@@

Though storing such a string would require roughly a petabyte of memory, representing it indirectly as a computation
takes very little space at all. To put it in perspective, that's roughly the size all music ever recorded,
described in less than a half a tweet\footnote{Based on the iTunes library featuring approximately 50 million songs
of approximately 4 megabytes each, and assuming it represents approximately a fifth of all recorded music. Tweets are
restricted to 140 characters.}.

We can use Clojure's macro facility to build a crude framework for comparing the size of descriptions and their
resulting values. The following two definitions are identical, save that \verb|description-length| is a macro and therefore
operates on the unevaluated expression that is passed to it.

@@

If there is no way to describe a value more concisely than the value itself, we say that it is random. In other words an
explanatory power of one or less is no explanation at all.

@@

Using a little more macro magic, we can calculate the ratio between the above description and the literal notes
of the song. The \verb|definitional| macro allows us to use the symbol \verb|row-row| in our fact notation, rather than
having to paste in the entire expression.
